---
title: "Spatial Indicators Summary"
subtitle: ""
author: "Peter Kidd & Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    number_section: true
    keep_md: true
mathjax: TRUE
fig_width: 6 
fig_height: 4 
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
bibliography: https://raw.githubusercontent.com/peterjosephkidd/SpatIndAssess/main/References/Refs.SpatindAssess.bib

#knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding, output_dir="html")})
#bibliography: bibliography.bib
---

```{r knitr, echo=FALSE, warning=FALSE, cache = FALSE}
pckgs <- c("knitr", "icesDatras", "icesVocab", "dplyr", "RCurl", "rvest", "maps", "ggplot2", "plotly", "devtools", "ineq", "zoo")

invisible(lapply(pckgs, library, warn.conflicts = F, quietly = T, character.only = T))


opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =!TRUE, 
               eval      =!TRUE,
               
               cache     =FALSE, 
               cache.path="cache/spatial/",
               
               fig.path  ="../tex/spatial-",
               fig.width =8,
               fig.height=6,
               dev       ="png")

options(digits=3)

iFig=0
iTab=0
```

[Jump to Introduction](#intro)

[Jump to Data Preparation](#prep)

  [Jump to Stock ple.27.420](#stk)

[Jump to Empirical Spatial Indicator Analysis](#esia)

  * [Jump to Location](#loc)
  
  * [Jump to Range](#range)
  
  * [Jump to Occupancy](#occ)
  
  * [Jump to Aggregation](#agg)

[Jump to More Information](#More)

[Jump to References](#References)

# Introduction {#intro}

This vignette provides an overview of spatial indicators used to estimate the location, range, occupancy, and aggregation of populations in the context of fisheries management.

## Data Preparation {#prep}

Spatial indicators are configured to work with DATRAS survey data. Load in some survey data and process it first before parsing through spatial indicator functions.

**Load DATRAS exchange data**

Here we load NS-IBTS Quarter 1 survey data for years 2018 to 2022. 

```{r data_load, echo = T, eval = T, cache = T}
yrs <- c(2000:2005)
qrs <- c(1)
srv <- "NS-IBTS"

hh  <- icesDatras::getDATRAS(record = "HH", srv, years = yrs, quarters = qrs)
hl <-  icesDatras::getDATRAS(record = "HL", srv, years = yrs, quarters = qrs)
ca  <- icesDatras::getDATRAS(record = "CA", srv, years = yrs, quarters = qrs) # for completeness, but not used
```
Remove duplicate rows in exchange data.

```{r data_rows, echo = T, eval = T, cache = T, dependson = "data_load"}
hh <- unique(hh)
hl <- unique(hl)
ca <- unique(ca)
```

**ICES Statistical Rectangles**

In the exchange data (in `hh` and `hl`) we know the ICES rectangle that each haul was conducted in, but we do not have the associated division. To be able to subset data to a specific stock region, we need to download [ICES Statistical Rectangle shapefile (Quick Downloads > ICES StatRec mapped to ICES Area)](https://gis.ices.dk/sf/index.html?widget=StatRec) and append information on ICES divisions to our exchange data. A download is available on GitHub and has been converted to a `.rds` file which is loaded in here.

```{r data_shp, echo = T, eval = T}
load(url("https://github.com/peterjosephkidd/SpatIndAssess/raw/main/Data/ICES%20Rect/ices_rect.rds"))
```
Add ICES Divisions

```{r data_merge, echo = T, eval = T}
area_div <- dplyr::distinct(ices_rect[c("ICESNAME", "Area_27", "Shape_Area")])
hh <- merge.data.frame(hh, area_div, by.x = "StatRec", by.y = "ICESNAME")
ca <- merge.data.frame(ca, area_div, by.x = "AreaCode", by.y = "ICESNAME")
```

**Basic Data Processing**

Remove invalid hauls:

```{r data_invhaul, echo = T, eval = T}
hh <- filter(hh, !HaulVal %in% c("I", "P")) # p = partly valid, it is deprecated 
```

`-9` is a placeholder for NAs. Change to `NA` for `TotalNo` column:

```{r data_nar, echo = T, eval = T}
hl$TotalNo[hl$TotalNo == -9] <- NA
```

Create haul.id:
```{r data_haulid, echo = T, eval = T}
hh$haul.id <- as.character(
  paste(hh$Year, hh$Quarter, hh$Country, hh$Ship, hh$Gear, hh$StNo, hh$HaulNo, 
        sep = ":"))
hl$haul.id <- as.character(
  paste(hl$Year, hl$Quarter, hl$Country, hl$Ship, hl$Gear, hl$StNo, hl$HaulNo, 
        sep = ":"))
ca$haul.id <- as.character(
  paste(ca$Year, ca$Quarter, ca$Country, ca$Ship, ca$Gear, ca$StNo, ca$HaulNo, 
        sep = ":"))
```


Merge haul information from `hh` with landings information in `hl`. 

```{r data_hlhh, echo = T, eval = T}
## Refine columns
m <- hh[c("haul.id", "Year", "Quarter", "Month", "Survey","Country", "Ship", 
          "Gear", "GearEx", "DoorType", "HaulDur", "HaulNo", "StNo", "SweepLngt", 
          "StatRec", "Area_27", "ShootLong", "ShootLat", "HaulVal", "Depth")]
## Merge HL with HH	
hlhh <- merge(hl, dplyr::distinct(m),
              c("haul.id", "Year", "Quarter", "HaulNo", "StNo", "Gear", "GearEx", 
                "DoorType","Ship", "SweepLngt", "Country", "Survey"))
rm(m)
```

[Back to Top](#top)

___

## Stock ple.27.420 {#stk}

Now that DATRAS survey data has been loaded and formatted, choose a stock to investigate and filter data accordingly. This example looks at European plaice (*Plueronectes platessa*) in Subarea 4 (North Sea) and Subdivision 20 (Skagerrak; [ple.27.420)](https://ices-library.figshare.com/articles/report/Plaice_Pleuronectes_platessa_in_Subarea_4_North_Sea_and_Subdivision_20_Skagerrak_Replacing_advice_provided_in_2022/22548568).

**Set parameters**
```{r stk, echo = T, eval = T}
# ple.27.420
species <- c("plaice", "Pleuronectes platessa")
species_aphia <- findAphia(species[2], latin = T)
stk_divs <- c("4.a", "4.b", "4.c", "3.a.20")
```

```{r stk_filter, echo = F, eval = F}
# Basic checks
hlhh.check <- filter(hlhh, 
               Valid_Aphia == species_aphia,
               Area_27 %in% stk_divs)

unique(hlhh.check$Valid_Aphia)
unique(hlhh.check$Area_27)
```
[Back to Top](#top)

___

# Empirical Spatial Indicator Analysis {#esia}
Suite of spatial indicator functions can be sourced from the `SpatIndAssess` GitHub repo:
```{r eval = T, echo = F}
# Function to create titles
ttl <- function(species, stk_divs, srv, qrs, yrs){
  paste0(species[1], " (", species[2], ") in ", paste0(stk_divs, collapse = ", "), "\n", srv, " (Q", qrs, ") ", min(yrs), " - ", max(yrs))
}
```

```{r esia, echo = T, eval = T}
# Source Spatial Indicator functions from GitHub
source("https://raw.githubusercontent.com/peterjosephkidd/SpatIndAssess/main/Functions/spatinds_funs.R", print.eval = F)
```

## Location {#loc}

### **Centre of Gravity (CoG):**

The CoG represents the mean location of the population [@woillez2009notes]. Here, *CoG* is calculated using the `x` and `y` coordinates of haul locations where the target species was identified (i.e. catch > 0). The mean of these `x` and `y` coordinates give *CoG (x)* and *CoG (y)*, respectively, which combine to give the point estimate of the populations mean location. Calculating *CoG* in this manner uses simple binary presence/absence data which ignores fish density at site locations. Instead, information on the number of target fish caught at each sample site can be used to weight the `x` and `y` coordinates in the calculation of *CoG (x)* and *CoG (y)*. As such, sites with high fish density will influence the *CoG* more than sites with low fish density. Whether to treat each sample site with target species catch > 0 as equal or to weight sample sites by fish density can be toggled on/off in `density` argument of the `coginis()` function. It is more typical to weight sites by density, but the option is there.

**An increase in *CoG (x)* indicates a shift Eastward, and increase in *CoG (y)* indicates a shift Northward.** 


```{r cg_calc, echo = T, eval = T}
cg <- coginis(hlhh, yrs, qrs, species_aphia, stk_divs, 
              iso = F, inertia = F, # toggle off outputting two another spatial indicators for now
              density = T) # weight hauls by  density of catch at each sample site (F therefore uses binary presence-absence data)

head(cg)
```
\n
The `cogplot()` function enables you to visualise the geographical trajectory of CoG over time. The resulting plot can also be passed through `ggplotly()` for interactivity and metadata.  
```{r cg_plot, echo = T, eval = T}
cg_p <-cogplot(cg, 
               grid = ices_rect, areas = stk_divs,
               xlim = c(-2, 6), ylim = c(52, 60)) 
suppressWarnings(ggplotly(cg_p, tooltip = "text"))
```

## Range {#range}

### **Inertia (I):** 

Inertia is the mean square distance between an individual survey site and the CoG, representing how dispersed the population is around its CoG [@woillez2009notes].  High values of inertia indicate that the population is widely spread across space. As with *CoG*, the inertia can be calculated by weighting samples by fish density. Inertia is therefore also sensitive to high density values [@woillez2009notes].

**An increase in *I* indicates that the population is distributed across a larger geographical region.**
```{r inert_calc, eval = T, echo = T}
inert <- coginis(hlhh, yrs, qrs, species_aphia, stk_divs, 
              iso = F, inertia = T, # inertia toggled on
              density = F) #

head(inert)
```
Plot the trend over time
```{r inert_plot, eval = T, echo = T}
in_p <- ggplot(data = inert, aes(x = Year, y = Inertia)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Inertia (I) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

in_p
```
No obvious trend

### **Extent of Occurrence (EOO):** 

EOO is a measure used by the International Union for Conservation of Nature (IUCN), defined as "*the area contained within the shortest continuous imaginary boundary which can be drawn to encompass all the known, inferred or projected sites of present occurrence of a taxon*" [@iucn_2012_eoo]. The `chullarea()` function draws a convex hull polygon around the survey sites with species occurrence and calculates the area of the polygon. Higher EOO indicates that the population is spread over a large geographical area.

**An increase in EOO indicates that that the population is distributed across a larger geographical region.**
```{r eoo_calc, eval = T, echo = T}
eoo <- chullarea(hlhh, yrs, qrs, species_aphia, stk_divs)[1:3] # this function needs tidying up, ignore other columns for now
head(eoo)
```

Plot the trend over time
```{r eoo_plot, eval = T, echo = T}
eoo_p <- ggplot(data = eoo, aes(x = Year, y = convex_hull_area)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  ylab("Extent of Occurence") +
  labs(title = "Extent of Occurence (EOO)",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

eoo_p
```


### **Ellipse Area (ELA):** 

ELA is similar in principle to EOO. Instead of a convex hull, the `ellarea()` function draws an ellipse around the survey sites with target species occurrence that encompasses 95% of the points. As with other range indicators, higher values indicate that the population is spread over a greater geographical region. ELA and EOO both use simple binary presence/absence data and are not sensitive to density values unlike Inertia. 

**An increase in ELA indicates that that the population is distributed across a larger geographical region.**
```{r ela_calc, eval = T, echo = T}
print(stk_divs)
ela <- ellarea(hlhh, yrs, qrs, species_aphia, stk_divs = stk_divs)
head(ela)
```

```{r ela_plot, eval = T, echo = T}
ela_p <- ggplot(data = ela, aes(x = Year, y = `Ellipse Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Ellipse Area (ELA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

ela_p
```

## Occupancy {#occ}

### **Proportion of Presence (POP):**
The two POP indicators of occupancy reported here are related to the Positive Area indicator noted by @woillez2009notes. Positive Area is the geographical area occupied by the target species where density > 0. 

#### **Rectangle (POPR):** 
POPR can be seen as a proportion of the Positive Area to the total area sampled. It is the number of ICES rectangles with target species density > 0 (`nrects_p`) relative to the number of ICES rectangles surveyed (`nrects`). 

**POPR ranges from 0 to 1 with lower values indicating that a smaller proportion of the surveyed area was occupied by the target species.**

```{r popr_calc, eval = T, echo = T}
popr <- pa_rect(hlhh, yrs, qrs, species_aphia, stk_divs)
head(popr)
```

```{r popr_plot, eval = T, echo = T}
popr_p <- ggplot(data = popr, aes(x = Year, y = `PosAreaR`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Presence in ICES Rectangles (POPR) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Proportion of Presence (Rectangle)")

popr_p
```

#### **Haul (POPH):** 
POPH calculates the number of individual hauls with species presence (`pr_hauls`) relative to the total number of hauls (`no.haul.ids`). POPH indicator is spatially implicit and treats hauls as area. Therefore, hauls must be well spatially distributed across the stock area for POPH to be informative (i.e. representative survey design). Both POPH and POPR are spatially implicit in that the geographical coordinates in which the hauls or rectangles with density > 0 occur does not influence calculation. 

**POPH ranges from 0 to 1 with lower values indicating that species were found in a smaller proportion of hauls.**
```{r poph_calc, eval = T, echo = T}
poph <- pa_haul(hlhh, yrs, qrs, species_aphia, stk_divs)
head(poph)
```

```{r poph_plot, eval = T, echo = T}
poph_p <- ggplot(data = poph, aes(x = Year, y = `PosAreaH`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Presence in Survey Hauls (POPR) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Proportion of Presence (Haul)")

poph_p
```

## Map Indicators 
The `mapdis()` function visualises the above range and occupancy indicators on a single map for one timepoint (e.g. year and quarter). The function can equally be used to visualise a single indicator. 
```{r mapdis, eval = T, echo = T}
mapdis(hlhh, yrs = 2022, qrs, species_aphia, stk_divs, ices_rect, # data & parameters
       cog = T, inertia = T, EOO = T, ELA = T, # indicator toggles
       density = T, # weight samples 
       title = "Plaice (Pleuronectes platessa)\nNS-IBTS", 
       xlim = c(-5,11), ylim = c(50, 62)) # plotting window
         
```


## Aggregation {#agg}

### **Gini Index:** 
Both the Gini Index and D95 are derived from a Lorenz curve. A Lorenz curve plots the cumulative proportion of areas against the cumulative proportion of biomass (e.g. @myers_flatfish_gini_1990). Survey data can be processed with the `lorenz_data()` function data in the format required to plot the Lorenz curve and calculate indicators. `lorenz_plot()` is used to produce the Lorenz curves for each year in the data. E.g.:

###### {#lorplot}
```{r lor_data, eval = T, echo = T}
lordat <- lorenz_data(hlhh, yrs, qrs, species_aphia, stk_divs)
lorenz_plot(lordat) + 
  theme_minimal() +
    theme(panel.border = element_rect(colour = "black", fill = NA)) + # function needs tidying
  geom_label(data = data.frame(), aes(label = "A", x = 0.6, y = 0.3)) +
  geom_label(data = data.frame(), aes(label = "B", x = 0.9, y = 0.125))

```

If population biomass is homogeneously distributed across ICES rectangles, the Lorenz curve would be equal to the identity function. If population biomass is highly concentrated in a few ICES rectangles (relative to the total sampled), then the Lorenz curve bends toward the bottom right of the plot. The Gini index is the two times the area between the identity function and the Lorenz curve (`A`).

$$\text{Gini} = \frac{A}{A+B} = \frac{A}{0.5} = 2A$$
For consistency with other aggregation indicators the Gini index reported from the `Gini()` function is equal to 1-Gini Index such that **lower values indicate concentration and higher values indicate a homogeneous distribution**. This is therefore equal to two times area below the Lorenz curve (2B).
```{r gini_calc, eval = T, echo = T}
gni <- Gini(lordat)
head(gni)
```

```{r gini_plot, eval = T, echo = T}
gni_p <- ggplot(data = gni, aes(x = Year, y = `Gini Index`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Gini Index Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

gni_p
```

### **D95:** 
We have adapted D95 from @rindorf2012 to represent the proportion of biomass found in 95% of the surveyed area. D95 can be derived from the [Lorenz curve](#lorplot) as the point where the Lorenz curve intersects the *vertical* black line. The choice of 0.95 is somewhat arbitrary and any value between 0 and 1 can be chosen. The `level` argument of the `d95()` function allows you to change this (e.g. level = 0.5 for D50).

**D95 ranges from 0 to 0.95, with 0 indicating that all individuals were recorded in 5% of the surveyed area (high aggregation) and 0.95 indicating that 95% of the population were recorded in 95% of the rectangles surveyed (uniform distribution)**.

```{r d95_calc, eval = T, echo = T}
D <- d95(lordat)
```

```{r d95_plot, eval = T, echo = T}
d95_p <- ggplot(data = D, aes(x = Year, y = `D95`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Catch in 95% of ICES Rectangles in Stock Region (D95) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

d95_p
```


### **Spreading Area (SA):**

SA is another indicator documented in @woillez2009notes and is similar to the Gini index. SA is two times the area below the Lorenz curve - notice that this is the same definition of 1-Gini index. The difference is in the y-axis of the Lorenz curve. For SA, the y-axis represents the cumulative area occupied as opposed to the cumulative **proportion** of area occupied [in the Gini index above](#lorplot). By changing the y-axis scale from a proportion to raw units (e.g. km), the SA is not influenced by zero density values. 

**Higher SA values indicate the population biomass is more uniformly distributed. Lower values indicates higher aggregation.**

```{r sa_calc, eval = T, echo = T}
sa_data <- spreadingarea_data(hlhh, yrs, qrs, species_aphia, stk_divs)
sa <- sa_data %>%
        group_by(Year) %>%
        summarise("Spreading Area" = spreadingarea_calc(TotalNo_Dur)) %>%
        mutate(Quarter = paste(as.character(sort(unique(sa_data$Quarter))), collapse = ", ")) %>% # add quarters
        relocate(Year, Quarter) 
head(sa)
```

```{r sa_plot, eval = T, echo = T}
sa_p <- ggplot(data = sa, aes(x = Year, y = `Spreading Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Spreading Area (SA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

sa_p
```

### **Equivalent Area (EA):** 

EA is the area that would be covered by a population with homogeneously distributed density (@bez2001, @woillez2009notes). It is a ratio of the total abundance to the mean density per individual (see @bez2001 for more details on its calculation). 

**Higher EA values indicate the population biomass is more uniformly distributed. Lower values indicates higher aggregation.**

```{r ea_calc, eval = T, echo = T}
ea <- sa_data %>%
        group_by(Year) %>%
        summarise("Equivalent Area" = equivalentarea(TotalNo_Dur)) %>%
        mutate(Quarter = paste(as.character(sort(unique(sa_data$Quarter))), collapse = ", ")) %>% # add quarters
        relocate(Year, Quarter)
head(ea)
```

```{r ea_plot, eval = T, echo = T}
ea_p <- ggplot(data = ea, aes(x = Year, y = `Equivalent Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Equivalent Area (EA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

ea_p
```


### **Spread of Participation Index (SPI):** 
The SPI compares the observed fish density in each rectangle to what would be expected from a homogeneously distributed population [@plowman2003]. Again, SPI value is 1-SPI (henceforth referred to as just SPI) for consistency with other indicators that higher values equates to uniformity. SPI therefore ranges from 0 to 1, with 0 indicating that the population is highly aggregated.

```{r spi_calc, eval = T, echo = T}
SPI <- spi(hlhh, yrs, qrs, species_aphia, stk_divs)[c(1,2,4)] # function needs tidying

head(SPI)
```

```{r spi_plot, eval = T, echo = T}
spi_p <- ggplot(data = SPI, aes(x = Year, y = `SPI.dur`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Spread of Participation Index (SPI) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Spread of Participation Index (SPI)")

spi_p
```

[Back to Top](#top)

## Plot Indicator Trends
Plot all the the timeseries of indicators to visualise and compare trends.
```{r trend_merge, eval = T, echo = T}
# List of dfs
df_list <- list(cg, inert, eoo, ela, popr, poph, gni, D, sa, ea, SPI) 

# Categorise indicators
loc <- c("CoG (x)", "CoG (y)")
ran <- c("Inertia", "EOO", "ELA")
occ <- c("POPR", "POPH")
agg <- c("Gini Index", "D95", "SA", "EA", "SPI")

# Merge all outputs into a single df
sidf <- Reduce(function(x, y) merge(x, y, all=TRUE), df_list) %>%
  select(-c(nrects, nrects_p, no_haul.ids, pr_hauls)) %>% # remove some cols
  rename(EOO = convex_hull_area,
         POPR = PosAreaR,
         POPH = PosAreaH,
         ELA = `Ellipse Area`,
         SPI = SPI.dur,
         SA = `Spreading Area`,
         EA = `Equivalent Area`) %>%
  tidyr::pivot_longer(cols = 3:14, names_to = "Indicator", values_to = "Value") %>%
   mutate(Type = case_when(
     Indicator %in% loc  ~ "Location",
     Indicator %in% ran  ~ "Range",
     Indicator %in% occ  ~ "Occupancy",
     Indicator %in% agg  ~ "Aggregation")) %>%
  mutate(Indicator = factor(Indicator, levels = c(loc, ran, occ, agg)))

head(sidf)
```

```{r trend_plot, eval = T, echo = T}
p <- ggplot(data = sidf, aes(x = Year, y = Value)) +
  geom_line(aes(colour = Type)) +
  scale_x_continuous(breaks = seq(from = min(unique(sidf$Year)), to = max(unique(sidf$Year)), by = 2)) +
  facet_wrap(vars(Indicator), scales = "free") +
  theme_minimal() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 6)
  ) +
  labs(title = "Spatial Indicator Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  ylab("Indicator Value")

ggplotly(p)
```

# More Information {#more}

-   For more information on the FLR Project for Quantitative Fisheries
    Science in R, visit the FLR webpage [^1].

[^1]: <http://flr-project.org>

## Author information

## Acknowledgements

## Software Versions

**`r version$version.string`**

-   FLCore: `r packageVersion('FLCore')`

-   ggplotFL: `r packageVersion('ggplotFL')`

-   ggplot2: `r packageVersion('ggplot2')`

**Compiled**: `r date()`

[Back to Top](#top)

# References {#references}

