---
title: "Spatial Indicators Summary"
subtitle: ""
author: "Peter Kidd & Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    number_section: true
mathjax: TRUE
fig_width: 6 
fig_height: 4 
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
#knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding, output_dir="html")})
#bibliography: bibliography.bib
---

```{r knitr, echo=FALSE, warning=FALSE, cache = FALSE}
pckgs <- c("knitr", "icesDatras", "icesVocab", "dplyr", "RCurl", "rvest", "maps", "ggplot2", "plotly", "devtools", "ineq", "zoo")

invisible(lapply(pckgs, library, warn.conflicts = F, quietly = T, character.only = T))


opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =!TRUE, 
               eval      =!TRUE,
               
               cache     =FALSE, 
               cache.path="cache/spatial/",
               
               fig.path  ="../tex/spatial-",
               fig.width =8,
               fig.height=6,
               dev       ="png")

options(digits=3)

iFig=0
iTab=0
```

[Jump to Introduction](#intro)

[Jump to Data Preparation](#prep)

  [Jump to Stock ple.27.420](#stk)

[Jump to Empirical Spatial Indicator Analysis](#esia)

  * [Jump to Location](#loc)
  
  * [Jump to Range](#range)
  
  * [Jump to Occupancy](#occ)
  
  * [Jump to Aggregation](#agg)

[Jump to More Information](#More)

[Jump to References](#References)

# Introduction {#intro}

This vignette provides an overview of spatial indicators used to estimate the location, range, occupancy, and aggregation of populations in the context of fisheries management.

## Data Preparation {#prep}

Spatial indicators are configured to work with DATRAS survey data. Load in some survey data and process it first before parsing through spatial indicator functions.

**Load DATRAS exchange data**

Here we load NS-IBTS Quarter 1 survey data for years 2018 to 2022. 

```{r data_load, echo = T, eval = T, cache = T}
yrs <- c(2020:2022)
qrs <- c(1)
srv <- "NS-IBTS"

hh  <- icesDatras::getDATRAS(record = "HH", srv, years = yrs, quarters = qrs)
hl <-  icesDatras::getDATRAS(record = "HL", srv, years = yrs, quarters = qrs)
ca  <- icesDatras::getDATRAS(record = "CA", srv, years = yrs, quarters = qrs) # for completeness, but not used
```
Remove duplicate rows in exchange data.

```{r data_rows, echo = T, eval = T, cache = T, dependson = "data_load"}
hh <- unique(hh)
hl <- unique(hl)
ca <- unique(ca)
```

**ICES Statistical Rectangles**

In the exchange data (in `hh` and `hl`) we know the ICES rectangle that each haul was conducted in, but we do not have the associated division. To be able to subset data to a specific stock region, we need to download [ICES Statistical Rectangle shapefile (Quick Downloads > ICES StatRec mapped to ICES Area)](https://gis.ices.dk/sf/index.html?widget=StatRec) and append information on ICES divisions to our exchange data. A download is available on GitHub and has been converted to a `.rds` file which is loaded in here.

```{r data_shp, echo = T, eval = T}
load(url("https://github.com/peterjosephkidd/SpatIndAssess/raw/main/Data/ICES%20Rect/ices_rect.rds"))
```
Add ICES Divisions

```{r data_merge, echo = T, eval = T, dependson = "data_load"}
area_div <- dplyr::distinct(ices_rect[c("ICESNAME", "Area_27", "Shape_Area")])
hh <- merge.data.frame(hh, area_div, by.x = "StatRec", by.y = "ICESNAME")
ca <- merge.data.frame(ca, area_div, by.x = "AreaCode", by.y = "ICESNAME")
```

**Basic Data Processing**

Remove invalid hauls:

```{r data_invhaul, echo = T, eval = T, dependson = "data_load"}
hh <- filter(hh, !HaulVal %in% c("I", "P")) # p = partly valid, it is deprecated 
```

`-9` is a placeholder for NAs. Change to `NA` for `TotalNo` column:

```{r data_nar, echo = T, eval = T, dependson = "data_load"}
hl$TotalNo[hl$TotalNo == -9] <- NA
```

Create haul.id:
```{r data_haulid, echo = T, eval = T, dependson = "data_load"}
hh$haul.id <- as.character(
  paste(hh$Year, hh$Quarter, hh$Country, hh$Ship, hh$Gear, hh$StNo, hh$HaulNo, 
        sep = ":"))
hl$haul.id <- as.character(
  paste(hl$Year, hl$Quarter, hl$Country, hl$Ship, hl$Gear, hl$StNo, hl$HaulNo, 
        sep = ":"))
ca$haul.id <- as.character(
  paste(ca$Year, ca$Quarter, ca$Country, ca$Ship, ca$Gear, ca$StNo, ca$HaulNo, 
        sep = ":"))
```


Merge haul information from `hh` with landings information in `hl`. 

```{r data_hlhh, echo = T, eval = T, dependson = "data_load"}
## Refine columns
m <- hh[c("haul.id", "Year", "Quarter", "Month", "Survey","Country", "Ship", 
          "Gear", "GearEx", "DoorType", "HaulDur", "HaulNo", "StNo", "SweepLngt", 
          "StatRec", "Area_27", "ShootLong", "ShootLat", "HaulVal", "Depth")]
## Merge HL with HH	
hlhh <- merge(hl, dplyr::distinct(m),
              c("haul.id", "Year", "Quarter", "HaulNo", "StNo", "Gear", "GearEx", 
                "DoorType","Ship", "SweepLngt", "Country", "Survey"))
rm(m)
```

[Back to Top](#top)

___

## Stock ple.27.420 {#stk}

Now that DATRAS survey data has been loaded and formatted, choose a stock to investigate and filter data accordingly. This example looks at European plaice (*Plueronectes platessa*) in Subarea 4 (North Sea) and Subdivision 20 (Skagerrak; [ple.27.420)](https://ices-library.figshare.com/articles/report/Plaice_Pleuronectes_platessa_in_Subarea_4_North_Sea_and_Subdivision_20_Skagerrak_Replacing_advice_provided_in_2022/22548568).

**Set parameters**
```{r stk, echo = T, eval = T, dependson = "data_load"}
# ple.27.420
species <- c("plaice", "Pleuronectes platessa")
species_aphia <- findAphia(species[2], latin = T)
stk_divs <- c("4.a", "4.b", "4.c", "3.a.20")
```

**Filter data**
```{r stk_filter, echo = F, eval = F, dependson = "data_load"}
hlhh <- filter(hlhh, 
               Valid_Aphia == species_aphia,
               Area_27 %in% stk_divs)
```

**Basic checks**
```{r stk_check, echo = F, eval = F, dependson = "data_load"}
unique(hlhh$Valid_Aphia)
unique(hlhh$Area_27)
```
[Back to Top](#top)

___

# Empirical Spatial Indicator Analysis {#esia}

```{r eval = T, echo = F, dependson = list("data_load", "stk")}
ttl <- function(species, stk_divs, srv, qrs, yrs){
  paste0(species[1], " (", species[2], ") in ", paste0(stk_divs, collapse = ", "), "\n", srv, " (Q", qrs, ") ", min(yrs), " - ", max(yrs))
}
```

```{r esia, echo = T, eval = T, dependson="data_load"}
# Source Spatial Indicator functions from GitHub
i <- 1
source("https://raw.githubusercontent.com/peterjosephkidd/SpatIndAssess/main/Functions/spatinds_funs.R", print.eval = F)
```

## Location {#loc}

### **Centre of Gravity (CGx, CGy):**

The mean longitudinal and latitudinal location of the population. Changes in CG indicate whether the mean location of the population is shifting eastward/westward (CGx) or northward/southward (CGy).

```{r cg_calc, echo = T, eval = T, dependson = list("data_load", "stk", "esia")}
cg <- coginis(hlhh, yrs, qrs, species_aphia, stk_divs, 
              iso = F, inertia = F, # toggle off outputting two another spatial indicators for now
              density = T) # weight hauls by  density of catch at each sample site (F therefore uses binary presence-absence data)

head(cg)
```

Visualise changes in `cg` over time 
```{r cg_plot, echo = T, eval = T, dependson = list("data_load", "stk", "esia")}
cg_p <-cogplot(cg, 
               # set grid = ices_rect for ICES rectangles -- takes time to load
               grid = ices_rect, areas = stk_divs,
               xlim = c(-2, 6), ylim = c(52, 60)) 
suppressWarnings(ggplotly(cg_p, tooltip = "text"))
```

## Range {#range}

### **Inertia (I):** 

Inertia describes the dispersion/variance of the population around its centre of gravity. High values of inertia indicate that the population is widely spread across space.

```{r inert_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
inert <- coginis(hlhh, yrs, qrs, species_aphia, stk_divs, 
              iso = F, inertia = T, # inertia toggled on
              density = T) #

head(inert)
```
Plot the trend over time
```{r inert_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
in_p <- ggplot(data = inert, aes(x = Year, y = Inertia)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Inertia (I) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

in_p
```


### **Extent of Occurrence (EOO):** 

A convex hull polygon is drawn around occurrence points (i.e. sample sites with catch of the target species \> 0). EOO is the area of the polygon. High EOO indicates that the population is spread over a large geographical area.
```{r eoo_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
eoo <- chullarea(hlhh, yrs, qrs, species_aphia, stk_divs)[1:3] # this function needs tidying up, ignore other columns for now
head(eoo)
```

Plot the trend over time
```{r eoo_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
eoo_p <- ggplot(data = eoo, aes(x = Year, y = convex_hull_area)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  ylab("Extent of Occurence") +
  labs(title = "Extent of Occurence (EOO)",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

eoo_p
```


### **Ellipse Area (ELA):** 

Similar to EOO. But instead of a convex hull, ELA calculates the area of an ellipse that encompasses 95% of the occurrence sites.
```{r ela_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
print(stk_divs)
ela <- ellarea(hlhh, yrs, qrs, species_aphia, stk_divs = stk_divs)
head(ela)
```
```{r ela_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
ela_p <- ggplot(data = ela, aes(x = Year, y = `Ellipse Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Ellipse Area (ELA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA))

ela_p
```

## Occupancy {#occ}

### **Proportion of Presence (POP):** 

Indicates the proportion of area occupied by the target species using binary presence-absence data.

#### **Rectangle (POPR):** 

The proportion of the ICES rectangles surveyed with a catch of the target species \> 0.
```{r popr_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
popr <- pa_rect(hlhh, yrs, qrs, species_aphia, stk_divs)
head(popr)
```

```{r popr_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
popr_p <- ggplot(data = popr, aes(x = Year, y = `PosAreaR`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Presence in ICES Rectangles (POPR) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Proportion of Presence (Rectangle)")

popr_p
```

#### **Haul (POPH):** 

The proportion of hauls with catch of the target species \> 0.

```{r poph_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
poph <- pa_haul(hlhh, yrs, qrs, species_aphia, stk_divs)
head(poph)
```

```{r poph_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
poph_p <- ggplot(data = poph, aes(x = Year, y = `PosAreaH`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Presence in Survey Hauls (POPR) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Proportion of Presence (Haul)")

poph_p
```

### Plotting 
The `mapdis()` function visualises the above range and occupancy indicators on a single map for one timepoint (e.g. year and quarter). The function can equally be used to visualise a single indicator. 
```{r mapdis, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
mapdis(hlhh, yrs = 2022, qrs, species_aphia, stk_divs, ices_rect, # data & parameters
       cog = T, inertia = T, EOO = T, ELA = T, # indicator toggles
       density = T, # weight samples 
       title = "Plaice (Pleuronected platessa)\nNS-IBTS", 
       xlim = c(-5,11), ylim = c(50, 62)) # plotting window
         
```


## Aggregation {#agg}

### **Gini Index:** 

Derived from a Lorenz curve. Ranges from 0 to 1, with 1 indicating that the population is uniformly distributed across surveyed rectangles, and 0 indicating that the population was recorded in one rectangle.

```{r lor_data, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
lordat <- lorenz_data(hlhh, yrs, qrs, species_aphia, stk_divs)
lorenz_plot(lordat) + 
  theme_minimal() +
    theme(panel.border = element_rect(colour = "black", fill = NA)) # function needs tidying
```

```{r gini_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
gni <- Gini(lordat)
head(gni)
```

```{r gini_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
gni_p <- ggplot(data = gni, aes(x = Year, y = `Gini Index`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Gini Index Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

gni_p
```

### **D95:** 

Represents the proportion of the population present in 95% of the area. Ranges from 0 to 0.95, with 0 indicating that all individuals were recorded in 5% of the surveyed area (high aggregation) and 0.95 indicating that 95% of the population were recorded in 95% of the rectangles surveyed (uniform distribution).

```{r d95_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
D <- d95(lordat)
```

```{r d95_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
d95_p <- ggplot(data = D, aes(x = Year, y = `D95`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Proportion of Catch in 95% of ICES Rectangles in Stock Region (D95) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

d95_p
```


### **Spreading Area (SA):**

Derived from cumulative frequency data. Measures the area occupied by the population, taking into account variations in fish density values. High values of SA indicate homogeneous spatial distribution.

```{r sa_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
sa_data <- spreadingarea_data(hlhh, yrs, qrs, species_aphia, stk_divs)
sa <- sa_data %>%
        group_by(Year) %>%
        summarise("Spreading Area" = spreadingarea_calc(TotalNo_Dur)) %>%
        mutate(Quarter = paste(as.character(sort(unique(sa_data$Quarter))), collapse = ", ")) %>% # add quarters
        relocate(Year, Quarter) 
head(sa)
```

```{r sa_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
sa_p <- ggplot(data = sa, aes(x = Year, y = `Spreading Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Spreading Area (SA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

sa_p
```

### **Equivalent Area (EA):** 

The area that would be covered by a population with homogeneously distributed density. It is equal to the mean density per individual.

```{r ea_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
ea <- sa_data %>%
        group_by(Year) %>%
        summarise("Equivalent Area" = equivalentarea(TotalNo_Dur)) %>%
        mutate(Quarter = paste(as.character(sort(unique(sa_data$Quarter))), collapse = ", ")) %>% # add quarters
        relocate(Year, Quarter)
head(ea)
```

```{r ea_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
ea_p <- ggplot(data = ea, aes(x = Year, y = `Equivalent Area`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Equivalent Area (EA) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) 

ea_p
```


### **Spread of Participation Index (SPI):** 

Compares the observed spatial density distribution to the density distribution expected from a homogeneously distributed population. Ranges from 0 to 1, with 0 indicating that the population was observed in only one ICES rectangle, and 1 indicating that the population density was uniformly distributed across ICES rectangles.

```{r spi_calc, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
SPI <- spi(hlhh, yrs, qrs, species_aphia, stk_divs)[c(1,2,4)] # function needs tidying

head(SPI)
```

```{r spi_plot, eval = T, echo = T, dependson = list("data_load", "stk", "esia")}
spi_p <- ggplot(data = SPI, aes(x = Year, y = `SPI.dur`)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = "Spread of Participation Index (SPI) Timeseries",
       subtitle = ttl(species, stk_divs, srv, qrs, yrs)) +
  theme(panel.border = element_rect(colour = "black", fill = NA)) +
  ylab("Spread of Participation Index (SPI)")

spi_p
```

[Back to Top](#top)

# More Information {#more}

-   For more information on the FLR Project for Quantitative Fisheries
    Science in R, visit the FLR webpage [^1].

[^1]: <http://flr-project.org>

## Author information

## Acknowledgements

## Software Versions

**`r version$version.string`**

-   FLCore: `r packageVersion('FLCore')`

-   ggplotFL: `r packageVersion('ggplotFL')`

-   ggplot2: `r packageVersion('ggplot2')`

**Compiled**: `r date()`

[Back to Top](#top)

# References {#references}

[Back to Top](#top)
