---
title: "Survey Data Processing"
author: "Peter Kidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    toc: true
    toc_float: true
    toc_collapsed: false
    number_section: true
    theme: journal
    highlight: zenburn
    df_print: paged
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, fig.align = "center", fig.width = 6, comment = ">", cache = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# To Do List
1. Check if I need a new shapefile for ICES areas to include area 6. Currently using same shapefile I used for Trilaterals which was focused just on the North Sea

# Prepare Workspace
```{r wd}
# rm(list = ls())
getwd()
getOption("download.file.method") # wininet causes errors
options(download.file.method = "curl")
```

# Load Packages & Functions
```{r}
pckgs <- c("icesDatras", "icesVocab", "rgdal", "ggplot2", "dplyr")
for(pkg in pckgs){
  library(pkg, character.only = T, quietly = T)
}
getwd()
rm(pckgs, pkg)
```

```{r}
source(paste0(getwd(),"/Functions/dataprep_funs.R")) # for dealing with datras data
```

# ICES Divisions and Rectangles 
```{r ices.rect, echo = T, eval = F}
### ICES Rectangles
ices_rect2 <- readOGR(dsn = paste0(getwd(), "/Data/ICES Rect"), layer = "StatRec_map_Areas_Full_20170124")
ices_rect <- makeReadableFortify(ices_rect2)

rm(ices_rect2)
```
```{r, save.rect, echo = F, eval = F}
save(ices_rect, file = paste0(getwd(), "/Data/ICES Rect/ices_rect.rds"))
```

```{r ices.divs, echo = T, eval = F}
### ICES Divisions
ices_divs2 <- readOGR(dsn = paste0(getwd(), "/Data/ICES Divs"), layer = "ICES_Areas_20160601_cut_dense_3857")
# ices_divs <- readOGR(dsn = "ICES North Sea Divisions", layer = "ICES_Divisons_CodHadWhgPok") # old shapefile
ices_divs <- makeReadableFortify(ices_divs2)

rm(ices_divs2)
```
```{r save.divs, eval = F, echo = F}
save(ices_divs, file = paste0(getwd(), "/Data/ICES Divs/ices_divs.rds"))
```

# Download, save, & process survey data
```{r}
#### Save location
surveydata.path <- "C:/Users/pk02/OneDrive - CEFAS/Projects/C8503B/PhD/DATRAS/Spatial Indicator R Project/Survey Data/"
surveydata.path <- "C:/Users/pk02/OneDrive - CEFAS/Projects/C8503B/PhD/spatind-1/boot/initial/data/surveys"
### Create directory for survey data
if(dir.exists(surveydata.path) == FALSE){
  dir.create(surveydata.path)
}
```

## NS-IBTS (G1022 [Q1] & G2829 [Q3])
North Sea international Bottom Trawl Survey Q1 & Q3

Survey years available
Q1: 1966-2022
Q3: 1991-2022

```{r save.nsibts, echo = F, eval = F}
#### Download data
ns_ibts.hh <- getDATRAS(record = "HH", "NS-IBTS", years = c(1966:2022), quarters = c(1,3))
ns_ibts.hl <- getDATRAS(record = "HL", "NS-IBTS", years = c(1966:2022), quarters = c(1,3))
ns_ibts.ca <- getDATRAS(record = "CA", "NS-IBTS", years = c(1966:2022), quarters = c(1,3))

### Create directory for NS-IBTS
if(dir.exists(paste0(surveydata.path, "NS-IBTS")) == FALSE){
  dir.create(paste0(surveydata.path, "NS-IBTS"))
}
save(ns_ibts.hh, file = paste0(surveydata.path, "NS-IBTS/ns_ibts.hh.rda"))
save(ns_ibts.hl, file = paste0(surveydata.path, "NS-IBTS/ns_ibts.hl.rda"))
save(ns_ibts.ca, file = paste0(surveydata.path, "NS-IBTS/ns_ibts.ca.rda"))

#### Processing NS-IBTS
load(paste0(surveydata.path, "NS-IBTS/ns_ibts.hh.rda"))
load(paste0(surveydata.path, "NS-IBTS/ns_ibts.hl.rda"))
load(paste0(surveydata.path, "NS-IBTS/ns_ibts.ca.rda"))

ns_ibts.data <- prepsurveydata(ns_ibts.hh, ns_ibts.hl, ns_ibts.ca, ices_rect)
rm(ns_ibts.hh, ns_ibts.hl, ns_ibts.ca)

### Save
save(ns_ibts.data, file = paste0(surveydata.path, "NS-IBTS/ns_ibts.data.rda"))
rm(ns_ibts.data)
```

>
>

## BTS (B2453)
Beam Trawl Survey - Southern North Sea, Irish Sean and Western Channel - BTS

Survey quarters available:
Q1
Q3
Q4

Survey years available:
1985-2022

```{r load.datras, echo = T, eval = F}
#### Download BTS
### icesDATRAS::getDATRAS (this takes a while)
bts.hh <- getDATRAS(record = "HH", "BTS", years = c(1985:2022), quarters = c(1,3,4))
bts.hl <- getDATRAS(record = "HL", "BTS", years = c(1985:2022), quarters = c(1,3,4))
bts.ca <- getDATRAS(record = "CA", "BTS", years = c(1985:2022), quarters = c(1,3,4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "BTS")) == FALSE){
  dir.create(paste0(surveydata.path, "BTS"))
}
save(bts.hh, file = paste0(surveydata.path, "BTS/bts.hh.rda"))
save(bts.hl, file = paste0(surveydata.path, "BTS/bts.hl.rda"))
save(bts.ca, file = paste0(surveydata.path, "BTS/bts.ca.rda"))

#### Processing BTS
load(paste0(surveydata.path, "BTS/bts.hh.rda"))
load(paste0(surveydata.path, "BTS/bts.hl.rda"))
load(paste0(surveydata.path, "BTS/bts.ca.rda"))

bts.data <- prepsurveydata(bts.hh, bts.hl, bts.ca, ices_rect)
rm(bts.hh, bts.hl, bts.ca)

### Save
save(bts.data, file = paste0(surveydata.path, "BTS/bts.data.rda"))
rm(bts.data)
```

>
>

## BTS-Isis (B2453)
Beam Trawl Survey - Ship Isis
Same survey as above. Filtered for Isis ship only?

Survey quarters available:
Q1
Q3
Q4

Survey years available:
1985-2022

```{r load.data, cache = F, echo=FALSE, eval=TRUE}
### Load BTS
load(paste0(surveydata.path, "BTS/bts.hh.rda"))
load(paste0(surveydata.path, "BTS/bts.hl.rda"))
load(paste0(surveydata.path, "BTS/bts.ca.rda"))

#### Filter BTS to ISIS ship
bts_isis.hh <- bts.hh[bts.hh$Ship == "64SS",]
bts_isis.hl <- bts.hl[bts.hl$Ship == "64SS",]
bts_isis.ca <- bts.ca[bts.ca$Ship == "64SS",]

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "BTS-Isis")) == FALSE){
  dir.create(paste0(surveydata.path, "BTS-Isis"))
}
save(bts_isis.hh, file = paste0(surveydata.path, "BTS-Isis/bts_isis.hh.rda"))
save(bts_isis.hl, file = paste0(surveydata.path, "BTS-Isis/bts_isis.hl.rda"))
save(bts_isis.ca, file = paste0(surveydata.path, "BTS-Isis/bts_isis.ca.rda"))

#### Processing BTS-Isis
load(paste0(surveydata.path, "BTS-Isis/bts_isis.hh.rda"))
load(paste0(surveydata.path, "BTS-Isis/bts_isis.hl.rda"))
load(paste0(surveydata.path, "BTS-Isis/bts_isis.ca.rda"))

bts_isis.data <- prepsurveydata(bts_isis.hh, bts_isis.hl, bts_isis.ca, ices_rect)
rm(bts_isis.hh, bts_isis.hl, bts_isis.ca)

### Save
save(bts_isis.data, file = paste0(surveydata.path, "BTS-Isis/bts_isis.data.rda"))
rm(bts_isis.data)
```

>
>

## UK-BTS (B2453)
Same survey as above.Filtered for UK vessels only?

Survey quarters available:
Q1
Q3
Q4

Survey years available:
1985-2022

```{r load.data, cache = F, echo=FALSE, eval=TRUE}
### Load BTS
load(paste0(surveydata.path, "BTS/bts.hh.rda"))
load(paste0(surveydata.path, "BTS/bts.hl.rda"))
load(paste0(surveydata.path, "BTS/bts.ca.rda"))
### Filter BTS
uk_bts.hh <- bts.hh[bts.hh$Country == "GB",]
uk_bts.hl <- bts.hl[bts.hl$Country == "GB",]
uk_bts.ca <- bts.ca[bts.ca$Country == "GB",]
### Create directory
if(dir.exists(paste0(surveydata.path, "UK-BTS")) == FALSE){
  dir.create(paste0(surveydata.path, "UK-BTS"))
}
save(uk_bts.hh, file = paste0(surveydata.path, "UK-BTS/uk_bts.hh.rda"))
save(uk_bts.hl, file = paste0(surveydata.path, "UK-BTS/uk_bts.hl.rda"))
save(uk_bts.ca, file = paste0(surveydata.path, "UK-BTS/uk_bts.ca.rda"))

#### Processing UK-BTS
load(paste0(surveydata.path, "UK-BTS/uk_bts.hh.rda"))
load(paste0(surveydata.path, "UK-BTS/uk_bts.hl.rda"))
load(paste0(surveydata.path, "UK-BTS/uk_bts.ca.rda"))

uk_bts.data <- prepsurveydata(uk_bts.hh, uk_bts.hl, uk_bts.ca, ices_rect)
rm(uk_bts.hh, uk_bts.hl, uk_bts.ca)

### Save
save(uk_bts.data, file = paste0(surveydata.path, "UK-BTS/uk_bts.data.rda"))
rm(uk_bts.data)
```

>
>

## SNS (B3499)
Sole Net Survey (SNS) Industry survey

Survey quarters available:
Q3

Survey years available:
1969-2022

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
sns.hh <- getDATRAS(record = "HH", "SNS", years = c(1969:2022), quarters = c(3))
sns.hl <- getDATRAS(record = "HL", "SNS", years = c(1969:2022), quarters = c(3))
sns.ca <- getDATRAS(record = "CA", "SNS", years = c(1969:2022), quarters = c(3))
### save data
# Create directory
if(dir.exists(paste0(surveydata.path, "SNS")) == FALSE){
  dir.create(paste0(surveydata.path, "SNS"))
}
save(sns.hh, file = paste0(surveydata.path, "SNS/sns.hh.rda"))
save(sns.hl, file = paste0(surveydata.path, "SNS/sns.hl.rda"))
save(sns.ca, file = paste0(surveydata.path, "SNS/sns.ca.rda"))

### Processing SNS
load(paste0(surveydata.path, "SNS/sns.hh.rda"))
load(paste0(surveydata.path, "SNS/sns.hl.rda"))
load(paste0(surveydata.path, "SNS/sns.ca.rda"))

sns.data <- prepsurveydata(sns.hh, sns.hl, sns.ca, ices_rect)
rm(sns.hh, sns.hl, sns.ca)

### Save
save(sns.data, file = paste0(surveydata.path, "SNS/sns.data.rda"))
rm(sns.data)
```

>
>

## YFS (B6805) [Doesnt exist in ICES Vocab look-up]
I think this should be the Demersal Young Fish Survey (DYFS, B7567)

Survey quarters available:
Q3
Q4

Survey years available:
1970-2020

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
dyfs.hh <- getDATRAS(record = "HH", "DYFS", years = c(1969:2022), quarters = c(3,4))
dyfs.hl <- getDATRAS(record = "HL", "DYFS", years = c(1969:2022), quarters = c(3,4))
dyfs.ca <- getDATRAS(record = "CA", "DYFS", years = c(1969:2022), quarters = c(3,4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "DYFS")) == FALSE){
  dir.create(paste0(surveydata.path, "DYFS"))
}
save(dyfs.hh, file = paste0(surveydata.path, "DYFS/dyfs.hh.rda"))
save(dyfs.hl, file = paste0(surveydata.path, "DYFS/dyfs.hl.rda"))
save(dyfs.ca, file = paste0(surveydata.path, "DYFS/dyfs.ca.rda"))

#### Processing DYFS
load(paste0(surveydata.path, "DYFS/dyfs.hh.rda"))
load(paste0(surveydata.path, "DYFS/dyfs.hl.rda"))
load(paste0(surveydata.path, "DYFS/dyfs.ca.rda"))

dyfs.data <- prepsurveydata(dyfs.hh, dyfs.hl, dyfs.ca, ices_rect) # Warning: merge not correct. Check
rm(dyfs.hh, dyfs.hl, dyfs.ca)
### Save
save(dyfs.data, file = paste0(surveydata.path, "DYFS/dyfs.data.rda"))
rm(dyfs.data)
```

>
>

## FR-YFS (B5507) [Doesnt exist in ICES Vocab look-up]
I think this should be the Demersal Young Fish Survey (DYFS, B7567)

Survey quarters available:
Q3
Q4

Survey years available:
1970-2020

>
>

## FR-CGFS (G3425) 
French Channel Groundfish Survey, FR-CGFS, Part of Western IBTS 4th quarter

Survey quarters available:
Q4

Survey years available:
1988-2022

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
fr_cgfs.hh <- getDATRAS(record = "HH", "FR-CGFS", years = c(1969:2022), quarters = c(4))
fr_cgfs.hl <- getDATRAS(record = "HL", "FR-CGFS", years = c(1969:2022), quarters = c(4))
fr_cgfs.ca <- getDATRAS(record = "CA", "FR-CGFS", years = c(1969:2022), quarters = c(4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "FR-CGFS")) == FALSE){
  dir.create(paste0(surveydata.path, "FR-CGFS"))
}
save(fr_cgfs.hh, file = paste0(surveydata.path, "FR-CGFS/fr_cgfs.hh.rda"))
save(fr_cgfs.hl, file = paste0(surveydata.path, "FR-CGFS/fr_cgfs.hl.rda"))
save(fr_cgfs.ca, file = paste0(surveydata.path, "FR-CGFS/fr_cgfs.ca.rda"))

#### Processing FR-CGFS
load(paste0(surveydata.path, "FR-CGFS/fr_cgfs.hh.rda"))
load(paste0(surveydata.path, "FR-CGFS/fr_cgfs.hl.rda"))
load(paste0(surveydata.path, "FR-CGFS/fr_cgfs.ca.rda"))

fr_cgfs.data <- prepsurveydata(fr_cgfs.hh, fr_cgfs.hl, fr_cgfs.ca, ices_rect)
rm(fr_cgfs.hh, fr_cgfs.hl, fr_cgfs.ca)

### Save
save(fr_cgfs.data, file = paste0(surveydata.path, "FR-CGFS/fr_cgfs.data.rda"))
rm(fr_cgfs.data)
```

>
>

## SWC-IBTS (G4299)
Scottish westcoast groundfish survey Q4 (Old) SWC-IBTS

Survey quarters available:
Q4

Survey years available:
1985-2010

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
swc_ibts.hh <- getDATRAS(record = "HH", "SWC-IBTS", years = c(1985:2010), quarters = c(1,4))
swc_ibts.hl <- getDATRAS(record = "HL", "SWC-IBTS", years = c(1985:2010), quarters = c(1,4))
swc_ibts.ca <- getDATRAS(record = "CA", "SWC-IBTS", years = c(1985:2010), quarters = c(1,4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "SWC-IBTS")) == FALSE){
  dir.create(paste0(surveydata.path, "SWC-IBTS"))
}

save(swc_ibts.hh, file = paste0(surveydata.path, "SWC-IBTS/swc_ibts.hh.rda"))
save(swc_ibts.hl, file = paste0(surveydata.path, "SWC-IBTS/swc_ibts.hl.rda"))
save(swc_ibts.ca, file = paste0(surveydata.path, "SWC-IBTS/swc_ibts.ca.rda"))

#### Processing SWC-IBTS
load(paste0(surveydata.path, "SWC-IBTS/swc_ibts.hh.rda"))
load(paste0(surveydata.path, "SWC-IBTS/swc_ibts.hl.rda"))
load(paste0(surveydata.path, "SWC-IBTS/swc_ibts.ca.rda"))

swc_ibts.data <- prepsurveydata(swc_ibts.hh, swc_ibts.hl, swc_ibts.ca, ices_rect)
rm(swc_ibts.hh, swc_ibts.hl, swc_ibts.ca)

### Save
save(swc_ibts.data, file = paste0(surveydata.path, "SWC-IBTS/swc_ibts.data.rda"))
rm(swc_ibts.data)
```

>
>

## SCOWCGFS (G4815)
Scottish Westcoast Groundfish Survey (SCOWCGFS) Quarter 4, Part of Western IBTS

Survey quarters available:
Q4

Survey years available:
2011-2022

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
scowcgfs.hh <- getDATRAS(record = "HH", "SCOWCGFS", years = c(2011:2022), quarters = c(1,2,3,4))
scowcgfs.hl <- getDATRAS(record = "HL", "SCOWCGFS", years = c(2011:2022), quarters = c(1,2,3,4))
scowcgfs.ca <- getDATRAS(record = "CA", "SCOWCGFS", years = c(2011:2022), quarters = c(1,2,3,4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "SCOWCGFS")) == FALSE){
  dir.create(paste0(surveydata.path, "SCOWCGFS"))
}
save(scowcgfs.hh, file = paste0(surveydata.path, "SCOWCGFS/scowcgfs.hh.rda"))
save(scowcgfs.hl, file = paste0(surveydata.path, "SCOWCGFS/scowcgfs.hl.rda"))
save(scowcgfs.ca, file = paste0(surveydata.path, "SCOWCGFS/scowcgfs.ca.rda"))

#### Processing SCOWCGFS
load(paste0(surveydata.path, "SCOWCGFS/scowcgfs.hh.rda"))
load(paste0(surveydata.path, "SCOWCGFS/scowcgfs.hl.rda"))
load(paste0(surveydata.path, "SCOWCGFS/scowcgfs.ca.rda"))

scowcgfs.data <- prepsurveydata(scowcgfs.hh, scowcgfs.hl, scowcgfs.ca, ices_rect)
rm(scowcgfs.hh, scowcgfs.hl, scowcgfs.ca)

### Save
save(scowcgfs.data, file = paste0(surveydata.path, "SCOWCGFS/scowcgfs.data.rda"))
rm(scowcgfs.data)
```

>
>

## IGFS (G7212)
Irish Groundfish Survey, IE-IGFS, Part of Western IBTS 4th quarter

Survey quarters available:
Q4

Survey years available:
2003-2022

```{r load.datras, echo = T, eval = F}
### icesDATRAS::getDATRAS (this takes a while)
ie_igfs.hh <- getDATRAS(record = "HH", "IE-IGFS", years = c(2003:2022), quarters = c(4))
ie_igfs.hl <- getDATRAS(record = "HL", "IE-IGFS", years = c(2003:2022), quarters = c(4))
ie_igfs.ca <- getDATRAS(record = "CA", "IE-IGFS", years = c(2003:2022), quarters = c(4))

#### Save
### Create directory
if(dir.exists(paste0(surveydata.path, "IE-IGFS")) == FALSE){
  dir.create(paste0(surveydata.path, "IE-IGFS"))
}

save(ie_igfs.hh, file = paste0(surveydata.path, "IE-IGFS/ie_igfs.hh.rda"))
save(ie_igfs.hl, file = paste0(surveydata.path, "IE-IGFS/ie_igfs.hl.rda"))
save(ie_igfs.ca, file = paste0(surveydata.path, "IE-IGFS/ie_igfs.ca.rda"))

#### Processing IE-IGFS
load(paste0(surveydata.path, "IE-IGFS/ie_igfs.hh.rda"))
load(paste0(surveydata.path, "IE-IGFS/ie_igfs.hl.rda"))
load(paste0(surveydata.path, "IE-IGFS/ie_igfs.ca.rda"))

ie_igfs.data <- prepsurveydata(ie_igfs.hh, ie_igfs.hl, ie_igfs.ca, ices_rect)
rm(ie_igfs.hh, ie_igfs.hl, ie_igfs.ca)

### Save
save(ie_igfs.data, file = paste0(surveydata.path, "IE-IGFS/ie_igfs.data.rda"))
rm(ie_igfs.data)
```
